Global Climate and Atmospheric Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and \Spitzer\ Phase Curve Observations

### 2018-04-02 ApJ_submit_v2/response.txt

10. Figure 6: Here again, I would like to see a different version or this version changed where the y-scaled on all of the plots are the same. It's hard to interpret the figure and the plots when having to mentally account for the changing y-scales for each of the different phases shown.

##

We explored using the same y-axis for all the panels in this figure, but found that the range has to be so large (0.1e-3 - 5e-3), that for some panels the shape of the spectra is hard to make out (particularly for phases near the dayside, when the planet-to-star flux is close to the top of this range).

To make it easier for readers to interpret the figure with a different y-axis on each panel, we added a 100 ppm error bar to the bottom right of each panel to illustrate the scale.

### 2018-04-02 ApJ_submit_v2/ms.tex
ref report

\subsubsection{\Spitzer\ Systematics}
\added{Warm Spitzer's primary systematic is intrapixel sensitivity variations, where the photometry depends on the precise location of the stellar center within its pixel.  We fit this systematic using the Bilinearly-Interpolated Subpixel Sensitivity (BLISS) mapping technique \citep{stevenson12}.  BLISS provides a flexible, non-analytic means to effectively weight the target flux by the spatial sensitivity variations within a pixel, while simultaneously fitting for other systematics and the physical parameters of the system. As demonstrated by \citet{Ingalls2016}, the POET pipeline with BLISS mapping can accurately model simulated \Spitzer\ light curves with known physical parameters and produce reliable results.}

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{fig5.pdf}
\caption{WASP-103b phase curve observations from \HST/WFC3 (top) and \Spitzer/IRAC (middle and bottom). For clarity, the data are phase-folded on the planet's orbital period and binned in 30 uniformly spaced bins between 0 and 1. The left column shows the phase curves with systematic noise removed (black points) compared to the best fit spherical harmonics model (colored lines). The error bars denote $1\,\sigma$ uncertainties (in some cases, the errors are smaller than the data points).  We include the transits in the fit, but they are not displayed in this figure. The right-hand column shows the binned residuals for the best-fit light curve.}
\label{fig:phasecurves}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{fig6.pdf}
\caption{Phase-resolved planet-to-star flux ratios (points) compared to the best fit blackbody (blue line) and the GCM with $\tau_\mathrm{drag4}$. Phases $\phi=0.5$ and $0.0$ correspond to times of secondary eclipse and transit, when the substellar and antistellar points are respectively aimed at Earth. The blackbody model is fit to the \HST/WFC3 data only. \added{We also plot a dotted horizontal line 1 ppt to draw attention to the changing limits on the y-axis.}}
\label{fig:spectra}
\end{figure*}

>>>>

\subsubsection{\Spitzer\ Systematics}
\added{Warm Spitzer's primary systematic is intrapixel sensitivity variation, where the photometry depends on the precise location of the stellar center within its pixel.  We fit this systematic using the Bilinearly-Interpolated Subpixel Sensitivity (BLISS) mapping technique \citep{stevenson12}.  BLISS provides a flexible, non-analytic means to effectively weight the target flux by the spatial sensitivity variations within a pixel, while simultaneously fitting for other systematics and the physical parameters of the system. As demonstrated by \citet{Ingalls2016}, the POET pipeline with BLISS mapping can accurately model simulated \Spitzer\ light curves with known physical parameters and produce reliable results.}

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{fig5.pdf}
\caption{WASP-103b phase curve observations from \HST/WFC3 (top) and \Spitzer/IRAC (middle and bottom). For clarity, the data are phase-folded on the planet's orbital period and binned in 30 uniformly spaced bins between 0 and 1. The left column shows the phase curves with systematic noise removed (black points) compared to the best fit spherical harmonics model (colored lines). The error bars denote $1\,\sigma$ uncertainties (in some cases, the errors are smaller than the data points).  We include the transits in the fit, but they are not displayed in this figure. The right-hand column shows the binned residuals for the best-fit light curve. \added{The gray error bars in the upper right of the left panels correspond to 500 ppm, to illustrate the changing y-axis scale.}}
\label{fig:phasecurves}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{fig6.pdf}
\caption{Phase-resolved planet-to-star flux ratios (points) compared to the best fit blackbody (blue line) and the GCM with $\tau_\mathrm{drag4}$. Phases $\phi=0.5$ and $0.0$ correspond to times of secondary eclipse and transit, when the substellar and antistellar points are respectively aimed at Earth. The blackbody model is fit to the \HST/WFC3 data only. \added{We also show a 100 ppm error bar in the lower right of each panel to emphasize the changing limits on the y-axes.}}
\label{fig:spectra}
\end{figure*}

### 2018-04-02 ms.tex
ref report

The photometric analyses are summarized for each observing season in Table\,\ref{tab:photometry}.  The standard deviations of a single observation with respect to the corresponding seasonal means are given in column~4; \added{the mean of the three standard deviations is 0.0058~mag, suggesting there is little night-to-night variation in WASP-103.  The three seasonal mean brightness values given in column 5 scatter about their grand mean with a standard deviation of 0.0036 mag, but we note that the most discrepant mean is from the third season, for which we have only partial coverage. Therefore, our results do not completely rule out low-level, year-to-year variability of 0.001~mag or so, but we cannot confirm this.}

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{fig6.pdf}
\caption{Phase-resolved planet-to-star flux ratios (points) compared to the best fit blackbody (blue line) and the GCM with $\tau_\mathrm{drag4}$. Phases $\phi=0.5$ and $0.0$ correspond to times of secondary eclipse and transit, when the substellar and antistellar points are respectively aimed at Earth. The blackbody model is fit to the \HST/WFC3 data only. \added{We also plot a dotted horizontal line 1 ppt to draw attention to the changing limits on the y-axis.}}
\label{fig:spectra}
\end{figure*}

>>>>

The photometric analyses are summarized for each observing season in Table\,\ref{tab:photometry}.  The standard deviations of a single observation with respect to the corresponding seasonal means are given in column~4; \added{the mean of the three standard deviations is 0.0058~mag, suggesting there is little night-to-night variation in WASP-103.  The three seasonal mean brightness values given in column 5 scatter about their grand mean with a standard deviation of 0.0036 mag, but we note that the most discrepant mean is from the third season, for which we have only partial coverage. Therefore, our results do not completely rule out low-level, year-to-year variability of $<0.001$~mag.}

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{fig6.pdf}
\caption{Phase-resolved planet-to-star flux ratios (points) compared to the best fit blackbody (blue line) and the GCM with $\tau_\mathrm{drag4}$. Phases $\phi=0.5$ and $0.0$ correspond to times of secondary eclipse and transit, when the substellar and antistellar points are respectively aimed at Earth. The blackbody model is fit to the \HST/WFC3 data only. \added{We also show a 100 ppm error bar in the lower right of each panel to draw attention to the changing limits on the y-axes.}}
\label{fig:spectra}
\end{figure*}
